Explicit Operations on Parametrised Polyhedra

### 2018-03-24 dcg-draft.tex
Revised version submitted to DCG on 24 March 2018 - see reply_to_reviewers.tex for details of the revision

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\span}{\text{span}}
\providecommand{\conv}{\text{conv}}
\providecommand{\epi}{\text{epi}}
\providecommand{\rk}[1]{\text{rank}\left(#1\right)}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\image}{im}

@@

\title{Explicit Operations on Parametrised Polytopes}%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{abstract}
The Pontryagin set difference is an operation between two sets that is used to calculate sets of safe operation in diverse applications including game theory and robust control.
%
We consider a particular class of set-valued maps; for this we introduce the property of parametric convexity and present some of its analytic framework.
%
In order to guarantee the convexity of the difference of a convex set and a set-valued map it proves necessary and sufficient that the set-valued map is parametrically convex.
%
For generic piecewise polyhedral set-valued maps we show that parametric convexity is equivalent to a constant combinatorial structure of all its realisations.
%
We present a computational method for verifying parametric convexity of a piecewise polyhedral set-valued map as well as a way to calculate the parametric Pontryagin difference between a polyhedron and a piecewise polyhedral set-valued map.
%
Two examples are given to illustrate the presented methodology.

\keywords{Parametric convexity \and Piecewise affine set-valued map \and Pontryagin difference \and Parametrised polytopes}

@@

\section{Introduction}
%
The Pontryagin difference was originally introduced (under the 
name Minkowski difference) as a set theoretic tool
in~\cite{Hadwiger:1950,Hadwiger:1957}. 
%However in the years since the term Minkowski difference has often been used to refer to a different operation.
%
It was implicitly reintroduced in the context of
differential games in~\cite{Pontryagin:1966}, where it was used to characterise safe sets for which strategies could be found which keep elements inside some second set for all possible adversary actions.
%
Since its introduction, the usage of the Pontryagin difference has been extended beyond applications in differential games to various scenarios in which safe sets are needed that withstand some perturbation.
%
See for example~\cite{blanchini:2007} for a its use as a robust
control analysis tool in several different contexts and under the name
(set-)erosion. It has also found use in morphological image analysis, e.g.~\cite{Haralick:1987}.
%

When the Pontryagin difference has to be performed explicitly by numerical algorithms, it is usually assumed that the respective sets are polytopic, since it is not possible to operate on general sets explicitly.
%
Algorithms to determine the Pontryagin difference between two
polytopes do not require more complex computation than the solving of
linear programs~\cite{Kolmanovsky:1998,Kerrigan:2003}, and their
analytical properties are well-known, see e.g.~\cite{blanchini:2007,Haralick:1987,Kolmanovsky:1998}.
%
The sets on which these operations can be performed are fixed
predetermined polytopes but, due to their physical interpretation in
terms of safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
%
For this purpose we consider the case in which the subtrahend is a
set-valued map with a polytopic realisation.

General set-valued maps have been studied analytically and various results are available in the literature, see e.g.~\cite{Aubin:2009}.
%
However, computational aspects of operations on general set-valued
maps are largely unknown. We refer to~\cite{Finzel:2000} for some results for polyhedral set-valued maps.
%
In this paper we present a particular class of set-valued map for which the Pontryagin difference can be computed explicitly.
%
The set-valued maps we consider are parametrised polytopes with a property we introduce as \emph{parametric convexity} which allows us to guarantee that the \emph{parametric Pontryagin difference} is convex for all convex minuend sets.
%
We provide the computational framework to allow us to perform parametric Pontryagin differences explicitly.

The paper is structured as follows:
%
In Section~\ref{sec:preliminaries} we summarise preliminaries that are
required throughout the paper. In
Section~\ref{sec:parametric:convexity} we introduce parametric
convexity, which is the essential ingredient for all subsequent
analysis, and provide analytic results for set operations. 
We refine and extend these results for the case of set-valued maps with polyhedral realisations in Section~\ref{sec:polyhedral:maps}.
%
Section~\ref{sec:computational:methods} elaborates on how to determine whether a polyhedral map is in fact parametrically convex and how to perform operations on such set-valued maps, these concepts are then illustrated in Section~\ref{sec:numerical:examples} by two examples and finally we conclude the paper in Section~\ref{sec:conclusion}.

Throughout this paper we refer to the the real $d$-dimensional parameter space as $Y\subseteq\mathbb R^d$, the $n$-dimensional realisation space as~$Z\subseteq\mathbb R^n$ and its power set~$\mathscr P(Z)$.
%
We denote the integer range~$\{1,\dots,m\}$ by~$\mathbb N_m$ and index sets by $\mathcal A,\,\mathcal J$ or $\mathcal I$, the complement of a subset of an index set $\mathcal I\subset\mathcal A$ is denoted by $\bar{\mathcal I}=\mathcal A\setminus\mathcal I$, the objects $a_{\mathcal I}$ and $b_{\mathcal I}$ denote the matrix and the column vector with rows given by the row vectors $a_i$ and the scalar values $b_i$ with $i\in\mathcal I$.
%
By $f\vert_\Omega$ we mean $f$ evaluated only $\Omega$, a ball centred around $c$ of radius $r$ is denoted by $B_r(z)=\{x:\norm{x-z}_2\leq\epsilon\}$ with the Euclidean norm $\norm{\cdot}_2$.
%
The Minkowski sum~\cite{Minkowski:1911} of the sets $X_1,X_2$ is denoted by $X_1\oplus X_2$, for a $d_2$ dimensional set $X$ the projection onto $\mathbb R^{d_1}$ with $d_1\leq d_2$ is denoted by $\pi_{d_1}(X) = \{x\in\mathbb R^{d_1}:\exists \tilde x\in\mathbb R^{d_2-d_1} (x,\tilde x)\in X\}$.
%
For a polytopic set $X$ the set of its vertices is denoted by $\text{vert}(X)$.
%
\section{Preliminaries}\label{sec:preliminaries}

Throughout the paper we deal with set-valued maps, i.e. functions that map an element of a metric space~$Y$ to a subset of a metric space~$Z$, that is $f:Y\mapsto\mathscr P(Z), Y\ni y\rightarrow f(y)\subset Z$. 
%
A detailed presentation on properties of set-valued maps is beyond the scope of this paper and we refer to~\cite{Aubin:2009}, here we only assume that the set-valued map is continuous in the sense that its \emph{graph}
%
\begin{equation}
  \mathscr G(f) = \{(y,z)\in Y\times Z: z\in f(y)\}
\end{equation}
%
has a continuous boundary, i.e. for every bounded point $(y,z)\in\partial\mathscr G(f)$ the boundary $\partial\mathscr G(f)$ is locally given by the graph of a continuous function.
%
We only consider set-valued maps with convex images, i.e. maps for which $z_1,z_2\in f(y)\Rightarrow \lambda z_1+(1-\lambda)z_2\in f(y)$ for all $\lambda\in[0,1]$ holds for all $y\in Y$.

An important subset of such set-valued maps are such that their realisations are polytopic, i.e. $f(y)$ is a polytope for all $y\in Y$, in particular we study maps which depend on the \emph{parameter} in a piecewise affine way.
%
The graph of such maps is given by a union of polytopes, they have been studied in~\cite{Finzel:2000}.
%
We will make statements about \emph{generic} such maps, that is properties which are structurally stable in the sense that if~$f(y)$ has a particular property than there exists an open neighbourhood $U\ni y$ such that $f(\tilde y)$ has the same property for all $\tilde y\in U$, furthermore the set of points for which the property does not hold is of measure zero.
%
In the course of this paper it will be self evident what the set of points is, where the property of interest fails, in particular a lower dimensional polyhedron and we therefore omit a measure theoretic treatment of our assumption.

The particular property we require is \emph{simplicity}, for each $y\in Y$ the set $f(y)$ is a polytope and each of its vertices~$v(y)$ is supported by a minimal number of hyperplanes, i.e. there exists a linear system defining the set~$f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $n$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
%
It is easy to see, that if $A(\cdot)$ and $b(\cdot)$ are continuous in $y$, then $\mathcal I$ locally defines a vertex, i.e. the combinatorial structure of a simple polytope is structurally stable and therefore being simple is a generic property of a polytope.

The induced graph~$G(P)$ of a polytope~$P$ is the graph with vertices and edges that coincide with the vertices and edges of the polytope itself~\cite{Bondy:2008}.
%
In this paper we only use one property of induced graphs, namely the \emph{Perles Conjecture}~\cite{Kalai:1988}:
\emph{For a simple polytope~$P$ the graph~$G(P)$ determines the combinatorial structure of~$P$.}

@@

In this section we define the property of \emph{parametric convexity} in the context of set-valued maps. 
%
This property is then used to demonstrate the convexity of a generalised Pontryagin difference operation (see e.g.~\cite{Hadwiger:1950,blanchini:2007}). 
%
% In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$.
%
\begin{definition}[Parametric Convexity]\label{def:parametric:convexity}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$, where $Y\ni p\mapsto \mathcal W(p) \subset Z$, be a continuous set-valued map. The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies
%
  \begin{equation}\label{eq:def:parametrically:convex}
  \mathcal W(\lambda p_1 + (1-\lambda)p_2)\subseteq\lambda \mathcal W(p_1) \oplus (1-\lambda) \mathcal W(p_2).
\end{equation}
for all $p_1,p_2\in Y$ and $\lambda\in (0,1)$.
\end{definition}
%
Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$. 
%
However, recall that we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$.
%
A similar definition was given in~\cite{Hadwiger:1957} for scalar families of sets ($d=1$), however the results presented are not directly related.

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
set-valued maps satisfying~\eqref{eq:def:parametrically:convex}.
%
This is based on a description of parametric convexity in terms of conditions on the graph~$\mathscr G(\mathcal W)$ of a set-valued map.
%
\begin{definition}\label{def:graph:of:map}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous set-valued map
such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
%
\begin{equation*}\begin{aligned}
\interior(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
\end{aligned}\end{equation*}
%
denotes the \emph{interior} of its graph and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \interior(\mathscr G(\mathcal W))
\]
%
its \emph{boundary};
%
\revision{furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{normal cone} is defined as}
%
\[
  \revision{\mathcal N_{\mathcal W} (p,z) = \{\zeta \in\mathbb R^n: \zeta^T (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .}
\]
%
\end{definition}
%
\begin{remark}
%
\revision{Note that the normal cone in Definition~\ref{def:graph:of:map} is defined in the space of the \emph{set variable} $z\in Y$ rather than \emph{graph variable} $(p,z)\in Y\times Z$.
%
Furthermore, the normal cone $\mathcal N_{\mathcal W} (p,z)$ is the set of normals to all hyperplanes that contain $z$ but no other points in $\mathcal W(p)$.}
%
\end{remark}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{theorem}\label{thm:p:convexity:graph}
  \revision{A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
  is parametrically convex iff
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in \interior (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$ and all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$ such that  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$.}
%
\end{theorem}
%
\begin{proof}
  %
  \revision{Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
  \[
    S = \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) 
      = \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
  \]
  % \begin{align*}
  %   S &= \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) \\
  %     &= \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
  % \end{align*}
  We first show that $z\in \partial S = S \setminus \interior(S)$ if and only if
  % \begin{equation}\label{eq:Scond}
  %   z = \lambda z_1 + (1 - \lambda) z_2
  %   \quad \text{and} \quad
  %   \mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset 
  % \end{equation}
  $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.}

>>>>

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\image}{im}
\DeclareMathOperator{\vertices}{vert}
\DeclareMathOperator*{\conv}{conv}
\DeclareMathOperator{\epi}{epi}

@@

\title{Explicit Operations on Parametrised Polyhedra}%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{abstract}
The Pontryagin set difference is an operation between two sets that is used to calculate sets of safe operation in diverse applications including game theory and robust control.
%
We consider a particular class of set-valued maps; for this we introduce the property of parametric convexity and present some of its analytic framework.
%
In order to guarantee the convexity of the difference of a convex set and a set-valued map it proves necessary and sufficient that the set-valued map is parametrically convex.
%
For generic piecewise polyhedral set-valued maps we show that parametric convexity is equivalent to a fixed combinatorial structure of all its realisations.
%
We present a computational method for verifying parametric convexity of a piecewise polyhedral set-valued map as well as a way to calculate the parametric Pontryagin difference between a polyhedron and a piecewise polyhedral set-valued map.
%
Two examples are given to illustrate the presented methodology.

\keywords{Parametric convexity \and Piecewise affine set-valued map \and Pontryagin difference \and Parametrised polyhedra}

@@

\section{Introduction}
%
The Pontryagin difference was originally introduced (under the 
name Minkowski difference) as a set theoretic tool
in~\cite{Hadwiger:1950,Hadwiger:1957}. 
%However in the years since the term Minkowski difference has often been used to refer to a different operation.
%
It was implicitly reintroduced in the context of
differential games in~\cite{Pontryagin:1966}, where it was used to characterise safe sets for which there exist strategies for restricting system parameters to desired sets for all possible adversary actions.
%
Since its introduction, the usage of the Pontryagin difference has been extended beyond applications in differential games to various scenarios in which safe sets are needed to withstand unknown disturbances.
%
For example~\cite{blanchini:2007} describes its use as a robust
control analysis tool in several different contexts under the name
(set-)erosion. It has also found use in morphological image analysis, e.g.~\cite{Haralick:1987}.
%

When the Pontryagin difference has to be performed explicitly by numerical algorithms, it is usually assumed that the respective sets are polyhedral, since it is not possible to operate on general sets explicitly.
%
Algorithms to determine the Pontryagin difference between two
polyhedra do not require more complex computation than the solution of
linear programs~\cite{Kolmanovsky:1998,Kerrigan:2003}, and their
analytical properties are well-known, see e.g.~\cite{blanchini:2007,Haralick:1987,Kolmanovsky:1998}.
%
The sets on which these operations can be performed are fixed
predetermined polyhedra but, due to their physical interpretation in
terms of safe sets, it can be desirable to extend the class of sets on which these operations can be performed.
%
For this purpose we consider the case in which the subtrahend is a
set-valued map with a polyhedral realisation.

General set-valued maps have been studied analytically and various results are available in the literature, see e.g.~\cite{Aubin:2009}.
%
However, computational aspects of operations on general set-valued
maps are largely unknown. We refer to~\cite{Finzel:2000} for some results for polyhedral set-valued maps.
%
In this paper we present a particular class of set-valued map for which the Pontryagin difference can be computed explicitly.
%
The set-valued maps we consider are parametrised polyhedra with a property we introduce as \emph{parametric convexity} which allows us to guarantee that the \emph{parametric Pontryagin difference} is convex for all convex minuend sets.
%
We also describe computational methods that allow the parametric Pontryagin difference to be determined explicitly.

\revision{To motivate the main issues addressed by this paper using a very simple example, consider the problem of determining the safe set for the state $x$ of a system in order to ensure that the successor state $x^+ = x + w$ lies in a given set $S$, where $w$ is the action of an adversary that satisfies $w\in\mathcal W$ for some known set $\mathcal W$. The safe set for $x$ in this problem is precisely the Pontryagin difference between $S$ and $\mathcal W$.
%
Now suppose that the adversary action $w$ is not independent of $x$ but instead belongs to a set $\mathcal W(x)$ that depends explicitly on $x$. In this case the safe region is the set of points $x$ satisfying $x+w\in S$ for all $w\in \mathcal W(x)$, which is by definition the parametric Pontryagin difference between the set $S$ and the set-valued map $\mathcal W(x)$. 
%
To be of use as a computational tool, the Pontryagin difference between a convex set $S$ and a set-valued map $\mathcal W(x)$ should be convex for a well-defined class of maps $\mathcal W(x)$; the paper characterizes this class by introducing the concept of and conditions for parametric convexity. 
%
In many applications the sets of interest are either polyhedral or bounded by polyhedra. The paper determines the conditions under which a polyhedral set-valued map is parametrically convex, discusses computational methods for checking parametric convexity, and describes how to compute the parametric Pontryagin difference between a polyhedron and a polyhedral set-valued map.
}

The paper is structured as follows:
%
In Section~\ref{sec:preliminaries} we summarise preliminaries that are
required throughout the paper. In
Section~\ref{sec:parametric:convexity} we introduce parametric
convexity, which is the essential ingredient for all subsequent
analysis, and provide analytic results for set operations. 
We refine and extend these results for the case of set-valued maps with polyhedral realisations in Section~\ref{sec:polyhedral:maps}.
%
Section~\ref{sec:computational:methods} elaborates on how to determine whether a polyhedral map is in fact parametrically convex and how to perform operations on such set-valued maps, these concepts are then illustrated in Section~\ref{sec:numerical:examples} by numerical examples and finally we conclude the paper in Section~\ref{sec:conclusion}.

Throughout this paper we refer to the real $d$-dimensional parameter space as $Y\subseteq\mathbb R^d$, the $n$-dimensional realisation space as~$Z\subseteq\mathbb R^n$ and its power set~$\mathscr P(Z)$.
%
We denote the integer range~$\{1,\dots,m\}$ as~$\mathbb N_m$, and symbols $\mathcal A$, $\mathcal I$ are used to denote index sets.
%, the complement of a subset of an index set $\mathcal A\subset\mathcal I$ is denoted $\bar{\mathcal A}=\mathcal I\setminus\mathcal A$.
%, the objects $a_{\mathcal I}$ and $b_{\mathcal I}$ denote the matrix and the column vector with rows given by the row vectors $a_i$ and the scalar values $b_i$ with $i\in\mathcal I$.
%
By $f\vert_\Omega$ we mean $f$ evaluated only on $\Omega$. The $n$-ball of radius $r$ centred at $c$ is denoted $B_r^n(c)=\{x\in\mathbb R^n :\norm{x-c}_2\leq r\}$, where $\norm{\cdot}_2$ is the Euclidean norm.
%
\revision{The Minkowski sum~\cite{Minkowski:1911} of sets $X_1,X_2\subset\mathbb R^n$ and their Pontryagin difference are respectively denoted
\begin{align*}
X_1\oplus X_2 &=\{x_1 + x_2 : x_1\in X_1, \, x_2\in X_2 \} , \\
X_1\ominus X_2 &=\{x\in\mathbb R^n : x + x_2 \in X_1, \, \forall x_2\in X_2\} .
% X_1\oplus X_2 &=\{x\in\mathbb R^n : \exists x_1\in X_1, \, x_2\in X_2 \text{ such that } x = x_1+x_2 \} . \\
% X_1\ominus X_2 &=\{x\in\mathbb R^n : x+x_2 \in X_1, \, \forall x_2\in X_2\} .
\end{align*}
%
The projection of a set $X\subset \mathbb R^{n_2}$ onto $\mathbb R^{n_1}$, with $n_1\leq n_2$, is denoted 
\[
\pi_{n_1}(X) = \{x\in\mathbb R^{n_1}: (x,\tilde x)\in X, \, \tilde x\in\mathbb R^{n_2-n_1} \}.
\]
%
We use the terms `polyhedron' and `polyhedral set' interchangeably to denote any set that can be expressed as the intersection of finitely many closed half-spaces in $\mathbb{R}^n$, for arbitrary $n$.
The set of all vertices of a polyhedral set $X$ is denoted $\vertices(X)$.}
%
\section{Preliminaries}\label{sec:preliminaries}

The paper makes extensive use of the concept of a set-valued map; this is a function $f$ that maps an element of the metric space~$Y$ to a subset of the metric space~$Z$, i.e.\ $f:Y\mapsto\mathscr P(Z), Y\ni y\rightarrow f(y)\subset Z$. 
%
We refer the reader to~\cite{Aubin:2009} for a detailed discussion of the properties of set-valued maps. Here we only assume that the set-valued map is continuous in the sense that its \emph{graph} 
%
\begin{equation}
  \mathscr G(f) = \{(y,z)\in Y\times Z: z\in f(y)\} 
\end{equation}
%
has a continuous boundary $\partial\mathscr G(f)$.
%, so that for every point $(y,z)\in\partial\mathscr G(f)$ the boundary $\partial\mathscr G(f)$ is locally given by the graph of a continuous function.
%
We consider only set-valued maps with convex images, namely maps with the property that, for all $y\in Y$, we have $\lambda z_1+(1-\lambda)z_2\in f(y)$ for all $\lambda\in[0,1]$ if $z_1,z_2\in f(y)$.
%
An important class of set-valued maps are those with polyhedral realisations, so that $f(y)$ is a polyhedron for all $y\in Y$, and in particular we study polyhedral set-valued maps which depend on the \emph{parameter} $y$ in a piecewise affine way.
%
The graph of a  piecewise affine polyhedral set-valued map is given by a union of polyhedra~\cite{Finzel:2000}.

\revision{In Sections~\ref{sec:polyhedral:maps} and~\ref{sec:computational:methods}
of this paper we consider \emph{generic} polyhedral set-valued maps, which are defined as follows.}

\begin{definition}[Generic polyhedral set-valued map]\label{def:generic_polyhedral_set}
\revision{The polyhedral set-valued map $f(y)$ is said to be generic if $f(y)$ is a \emph{simple} polyhedron for all $y\in Y$ (except possibly on a subset of $Y$ of zero measure), and if $f(y)$ is \emph{structurally stable}. For given $y\in Y$, the polyhedral set $f(y) = \{z: a_i(y)z\leq b_i(y)\, \forall i\in \mathcal I\}\subset \mathbb R^n$ is simple if each of its vertices is supported by a minimal number of hyperplanes, i.e.~if for each vertex $v(y)$ there exists an index set $\mathcal A\subset \mathcal I$, with $\lvert \mathcal A\rvert = n$, such that $a_i(y)v(y)=b_i(y)$ for all $i\in\mathcal A$ and $a_i(y)v(y)<b_i(y)$ for all $i\in \mathcal I \setminus \mathcal A$.
%
Furthermore $f(y)$ is structurally stable if the combinatorial structure of $f(y)$ is unchanged when the functions $a_i(y)$, $b_i(y)$ are replaced by perturbed versions $a_i(y) + \epsilon u^{\!\top}$, $b_i(y)+\epsilon s$, for arbitrary $u\in B_1^n(0)$ and $s\in B_1^1(0)$, 
whenever $\epsilon> 0$ is sufficiently small.}
\end{definition}

% \revision{In Sections~\ref{sec:polyhedral:maps} and~\ref{sec:computational:methods}
% of this paper we consider \emph{generic} polyhedral set-valued maps, by which we mean set-valued maps with the properties that $f(y)$ is a \emph{simple} polyhedron for all $y\in Y$ (except possibly on a subset of $Y$ of zero measure), and that $f(y)$ is \emph{structurally stable}. The polyhedral set $f(y) = \{z: a_i(y)z\leq b_i(y)\, \forall i\in \mathcal I\}\subset \mathbb R^n$ is simple if each of its vertices is supported by a minimal number of hyperplanes, i.e.~if for each vertex $v(y)$ there exists an index set $\mathcal A\subset \mathcal I$, with $\lvert \mathcal A\rvert = n$, such that $a_i(y)v(y)=b_i(y)$ for all $i\in\mathcal A$ and $a_i(y)v(y)<b_i(y)$ for all $i\in \mathcal I \setminus \mathcal A$.
% %
% Furthermore we say that $f(y)$ is structurally stable if the combinatorial structure of $f(y)$ does not vary as $y$ varies over the interior of $Y$.}

%
% We note that $f(y)$ is simple almost everywhere in $Y$ if and only if it has a fixed number of vertices and rays for all $y\in Y$ except possibly on a subset of $Y$ with measure zero (i.e.~ a lower-dimensional polyhedron).}
%
%in the sense that if $f(y)$ is simple, then there exists a neighbourhood, $U$, of $y$ such that $f(\tilde y)$ is simple for all $\tilde y\in U$, and furthermore any subset of $Y$ on which $f(y)$ is not simple must be of measure zero (i.e.~a lower-dimensional polyhedron).}

% It is easy to see that if $A(\cdot)$ and $b(\cdot)$ are continuous in $y$, then $\mathcal I$ locally defines a vertex, i.e. the combinatorial structure of a simple polyhedron is structurally stable and therefore being simple is a generic property of a polyhedron.
% zero measure.
%
%In our analysis it will be self-evident what the set of points is, where the property of interest fails, in particular a lower dimensional polyhedron and we therefore omit a measure theoretic treatment of our assumption.
%
% The particular property we require is \emph{simplicity}, namely that for each $y\in Y$ the set $f(y)$ is a polyhedron and each of its vertices~$v(y)$ is supported by a minimal number of hyperplanes, i.e.~there exists a linear system defining the set $f(y) = \{z:A(y)z\leq b(y)\}$ and each vertex $v(y)$ is defined by $n$ hyperplanes $A_{\mathcal I}(y)v(y)=b_{\mathcal I}(y)$ and $A_{\bar{\mathcal I}}(y)v(y)<b_{\bar{\mathcal I}}(y)$.
% %
% It is easy to see that if $A(\cdot)$ and $b(\cdot)$ are continuous in $y$, then $\mathcal I$ locally defines a vertex, i.e. the combinatorial structure of a simple polyhedron is structurally stable and therefore being simple is a generic property of a polyhedron.

The induced graph~$G(P)$ of a polyhedron~$P$ is the graph with vertices and edges that coincide with the vertices and edges of the polyhedron itself~\cite{Bondy:2008}.
%
In this paper we only use one property of induced graphs, 
\revision{namely the \emph{Perles Conjecture} proved in~\cite{blind87} and~\cite{Kalai:1988}, which can be stated as follows:}
\emph{For a simple polytope~$P$ the graph~$G(P)$ determines the combinatorial structure of~$P$.}

@@

In this section we first define the property of \emph{parametric convexity} in the context of set-valued maps,
%
then we use this property to demonstrate the convexity of a generalised Pontryagin difference operation (see e.g.~\cite{Hadwiger:1950,blanchini:2007}). 
%
% In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$.
%
\begin{definition}[Parametric Convexity]\label{def:parametric:convexity}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$, where $Y\ni p\mapsto \mathcal W(p) \subset Z$, be a continuous set-valued map. The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies
%
  \begin{equation}\label{eq:def:parametrically:convex}
  \mathcal W(\lambda p_1 + (1-\lambda)p_2)\subseteq\lambda \mathcal W(p_1) \oplus (1-\lambda) \mathcal W(p_2).
\end{equation}
for all $p_1,p_2\in Y$ and $\lambda\in (0,1)$.
\end{definition}
%
Although Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$, we only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$ in the remainder of this paper.
%
\revision{We note that a similar definition is given in~\cite{Hadwiger:1957} for scalar families of sets ($d=1$), and set-valued maps satisfying~(\ref{eq:def:parametrically:convex}) are called \emph{concave} in~\cite{wasowicz16}, however in both cases the results presented are not directly related to the topic of this paper.}

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
set-valued maps satisfying~\eqref{eq:def:parametrically:convex}.
%
This is based on a description of parametric convexity in terms of conditions on the graph~$\mathscr G(\mathcal W)$ of a set-valued map.
%
\begin{definition}\label{def:graph:of:map}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous set-valued map
such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
%
\begin{equation*}\begin{aligned}
\interior(\mathscr G(\mathcal W)) = \{(p,z) \in Y\times Z : \forall \zeta\in\mathbb R^n\;\exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \}
\end{aligned}\end{equation*}
%
denotes the \emph{interior} of its graph and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \interior(\mathscr G(\mathcal W))
\]
%
its \emph{boundary};
%
\revision{furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{normal cone} is defined as}
%
\[
  \revision{\mathcal N_{\mathcal W} (p,z) = \{v \in\mathbb R^n: v^\top (y - z) \leq 0, \;  \forall y\in \mathcal W(p) \} .}
\]
%
\end{definition}
%
\begin{remark}
%
\revision{The normal cone $\mathcal N_{\mathcal W} (p,z)$  in  Definition~\ref{def:graph:of:map} belongs to the same space as $z$ rather than the space of the graph variable $(p,z)$; it consists of normals of hyperplanes in $\mathbb R^n$ that contain $z$ but no points in the interior of $\mathcal W(p)$.}
%
\end{remark}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{lemma}\label{lem:p:convexity:graph}
  \revision{A set-valued map $\mathcal W$ satisfying $\mathcal W(p)\ni 0$ for all $p\in Y$
  is parametrically convex iff
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in \interior (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$ and all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$ such that  $\mathcal N_{\mathcal W}(p_1,z_1)\cap\mathcal N_{\mathcal W}(p_2,z_2)\neq\emptyset$.}
%
\end{lemma}
%
\begin{proof}\def\W{\mathcal{W}}\def\N{\mathcal{N}}
% 
  \revision{
    Consider the set $S$, defined for given $\lambda\in (0,1)$ and $p_1,p_2\in Y$ by
    \[
      S = \lambda \mathcal{W}(p_1) \oplus (1-\lambda) \mathcal{W}(p_2) 
      = \bigl\{ z : \lambda z_1 + (1 - \lambda) z_2, \ z_1 \in\mathcal W(p_1), \ z_2 \in\mathcal W(p_2) \bigr\} .
    \]
    We first show that $z\in \partial S = S \setminus \interior(S)$ if and only if
    $z = \lambda z_1 + (1 - \lambda) z_2$ for some $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ such that $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$.}

  \revision{If $z\in\partial S$, then there must exist $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$, which implies that it is not possible to find $z_1^\prime\in \mathcal{W}(p_1)$ and $z_2^\prime\in \mathcal{W}(p_2)$ such that $z + \epsilon \zeta =  \lambda z_1^\prime + (1 - \lambda) z_2^\prime$ for all $\epsilon > 0$. Hence $z_1\in\partial\W(p_1)$ and $z_2\in\partial\W(p_2)$ are necessary conditions for $z\in\partial S$.}
